Automated topic naming to support cross-project analysis of software maintenance activities

### 2011-03-26 msr/msr2011.tex
added General Terms
back to where I started?
updated the fonts

% Only for camera ready -- prevent TeX from rendering widows
\widowpenalty=9999
\clubpenalty=9999

@@

\conferenceinfo{MSR}{'11 Waikiki, Hawaii, USA}

@@

@@

%\terms{Theory}

@@

\newpage

@@

To evaluate our approach, we sought candidate systems that were mature projects and had openly accessible source control repositories. 
We selected systems from the same application domain, to control for differences in functional, rather than non-functional, requirements. 
We selected MySQL 3.23 and MaxDB 7.500 as they were open-source, partially-commercial database systems. 
MaxDB started in the late 1970s as a research project, and was later acquired by SAP. 
As of version 7.500, released April 2007, the project has over $940,000$ lines of C source code\footnote{generated using David A. Wheeler's \emph{SLOCCount}, \tiny{http://dwheeler.com/sloccount}.}. 
The MySQL project started in 1994 and MySQL 3.23 was released in early 2001. 
MySQL contains $320,000$ lines of C and C++ source code.  
%Choosing an older version of these projects allowed us to focus on projects which have moved further into the maintenance phase of the software life-cycle.
We explicitly chose older versions of mature projects from a stable problem domain to increase the likelihood that we would encounter primarily maintenance activities in our studies.

@@

%FAT
\newpage

@@

%FAT we can remove this
\newpage
\begin{quotation}
\small \noindent \textsf{
integrity, security,
interoperability, testability, maintainability, traceability,
accuracy, modifiability, understandability, availability, modularity,
usability, correctness, performance, verifiability, efficiency,
portability, flexibility, reliability.
}
\end{quotation}

@@

%FAT
\balance
\newpage

@@

@@

\subfloat[MaxDB 7.500]{                                 
\includegraphics[width=\textwidth]{figures/maxdb-timeline}
\label{fig:maxdb-timeline}
}
	\caption[]{NFR label per period. Each cell represents a 30-day period. %Numbers represent number of topics in that period labelled with that NFR. 
	Grid cell intensity (saturation) is mapped to label frequency
        relative to the largest label count of \emph{all} NFRs. Grey
        histogram bars indicate label frequency relative to that
        particular NFR's largest label count. Dashed vertical lines
        relate a project milestone (a \emph{key event}) to our topic windows. 
% \todo[inline]{better discussion}
}
\label{fig:timelines}
\end{figure*}

@@

%FAT
\newpage

\subsection{Do  projects differ in their relative  topic interest?}
%\subsubsection{Do  projects differ in their relative  topic interest?}
%\noindent\textbf{2. Do  projects differ in their relative  topic interest?} ---
Yes. MySQL 3.23 had proportionally more
topics labelled \emph{functionality}, while MaxDB had proportionally more
\emph{efficiency} related topics. MaxDB was a very mature release ``donated'' to the open-source community, 
whereas MySQL was in its relative infancy, and  
security problems were more common (security is a component of \emph{functionality} in the ISO9126 model). 
In both cases \emph{portability} was a constant maintenance concern and was prevalent throughout the lifetime of the projects. It may surprise developers how often portability arises as a concern.
%On one hand, this analysis is unsurprising; on the other hand, it provides confirmation that our approach identifies actual patterns.
%\subsection{Summary}

@@

\balance
\newpage

>>>>

% Only for camera ready -- prevent TeX from rendering widows
%\widowpenalty=9999
%\clubpenalty=9999
\clubpenalty = 10000
\widowpenalty = 10000
\displaywidowpenalty = 10000

@@

\conferenceinfo{MSR}{'11, May 21-22, 2011, Waikiki, Honolulu, HI, USA}
\CopyrightYear{2011}
\crdata{978-1-4503-0574-7/11/05}

@@

\vspace*{-0.4em}

@@

\vspace*{-1em}

\terms{Human Factors, Management, Measurement}

@@

@@

To evaluate our approach, we sought candidate systems that were mature projects and had openly accessible source control repositories. 
We selected systems from the same application domain, to control for differences in functional, rather than non-functional, requirements. 
We selected MySQL 3.23 and MaxDB 7.500 as they were open-source, partially-commercial database systems. 
MaxDB started in the late 1970s as a research project, and was later acquired by SAP. 
As of version 7.500, released April 2007, the project has over $940,000$ lines of C source code\footnote{generated using David A. Wheeler's \emph{SLOCCount}, {http://dwheeler.com/sloccount}.}. 
The MySQL project started in 1994 and MySQL 3.23 was released in early 2001. 
MySQL contains $320,000$ lines of C and C++ source code.  
%Choosing an older version of these projects allowed us to focus on projects which have moved further into the maintenance phase of the software life-cycle.
We explicitly chose older versions of mature projects from a stable problem domain to increase the likelihood that we would encounter primarily maintenance activities in our studies.

@@

@@

%FAT we can remove this
%\balance
%LFAT
\newpage
\begin{quotation}
\small \noindent \textsf{
integrity, security,
interoperability, testability, maintainability, traceability,
accuracy, modifiability, understandability, availability, modularity,
usability, correctness, performance, verifiability, efficiency,
portability, flexibility, reliability.
}
\end{quotation}

@@

%LFAT
\balance
\newpage

@@

%\balance

@@

\subfloat[MaxDB 7.500]{                                 
\includegraphics[width=\textwidth]{figures/maxdb-timeline}
\label{fig:maxdb-timeline}
}
	\caption[]{NFR label per period. Each cell represents a 30-day period. %Numbers represent number of topics in that period labelled with that NFR. 
	Grid cell intensity (saturation) is mapped to label frequency
        relative to the largest label count of \emph{all} NFRs. Grey
        histogram bars indicate label frequency relative to that
        particular NFR's largest label count. Dashed vertical lines
        relate a project milestone (\emph{*Key events*}) to our topic windows. 
% \todo[inline]{better discussion}
}
\label{fig:timelines}
\end{figure*}

@@

%LFAT
\balance
\newpage
\subsection{Do projects differ in their relative  topic interest?}
%\subsubsection{Do  projects differ in their relative  topic interest?}
%\noindent\textbf{2. Do  projects differ in their relative  topic interest?} ---
Yes. MySQL 3.23 had proportionally more
topics labelled \emph{functionality}, while MaxDB had proportionally more
\emph{efficiency} related topics. MaxDB was a very mature release ``donated'' to the open-source community, 
whereas MySQL was in its relative infancy, and  
security problems were more common (security is a component of \emph{functionality} in the ISO9126 model). 
In both cases \emph{portability} was a constant maintenance concern and was prevalent throughout the lifetime of the projects. It may surprise developers how often portability arises as a concern.
%On one hand, this analysis is unsurprising; on the other hand, it provides confirmation that our approach identifies actual patterns.
%\subsection{Summary}

@@

%LFAT
\balance
\newpage
